Done

### 2025-01-06 done.qmd
update

>>>>

2024-12-23: Made a webscraping bot on mastodon: [https://mastodon.social/@PAXscraper](https://mastodon.social/@PAXscraper), which reports stats from PsyArXiv:

<img src="images/PAXdec2024.png" height = 400>

2024-11-28/29: Represented [UKRN](https://www.ukrn.org/) at the [Swiss National Science Foundation](https://www.snf.ch/en)'s Research on Research Conference, Bern.

2024-10-23: Inaugural event of the [AFIRE Funder Forum](https://researchonresearch.org/afire-funders-forum/)

2024-10-07: Nature editorial on our project with VolkswagenStiftung: [New peer-review trial lets grant applicants evaluate each other’s proposals](https://www.nature.com/articles/d41586-024-03106-w)

2024-09: Trip to China. News story on this: [Navigating Research Culture and Funding Practices: Highlights from Shanghai](https://researchonresearch.org/shanghai-forum-tom-stafford-afire/)

2024-08-30: Article in New Scientist with Kate Dommett: [Is digital technology really swaying voters and undermining democracy?](https://www.newscientist.com/article/mg26335062-800-is-digital-technology-really-swaying-voters-and-undermining-democracy/). My [newsletter on this](https://tomstafford.substack.com/p/the-truth-about-digital-propaganda)
